---
title: "Data Cleaning Steps"
date: " `r format(Sys.Date(),  '%d %B %Y')`"
always_allow_html: yes
output:
  html_document:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    toc: yes
    toc_depth: 2
    toc_float: yes
    includes:
       in_header: css/header.html
---



<link rel="stylesheet" href="css/unhcr-bootstrap.css">
<link rel="stylesheet" href="css/style.css">
<link rel="stylesheet" href="css/unhcr-header.css">


# Data Cleaning Review

```{r loaddata, message=FALSE, warning=FALSE}
library(readr)
library(readxl)
library(dplyr)
library(stringr)
library(scales)
library(classInt)
library(ggplot2)
library(ggrepel)

mainDir <- getwd()
mainDirroot <- substring(mainDir, 0 , nchar(mainDir) - 5)
MainDataFrame <- read_delim(paste0(mainDirroot,"/data/MainDataFrame_raw.csv"),";", escape_double = FALSE, col_types = cols(today = col_date(format = "%Y-%m-%d")), trim_ws = TRUE)
```


## Counting initial # of Records

```{r message=FALSE, comment = ""}
nrow(MainDataFrame)
```


## Remove incomplete records

```{r message=FALSE, comment = ""}
MainDataFrame <- MainDataFrame[ !(is.na(MainDataFrame$end_mins1)) ,  ]
nrow(MainDataFrame)

```


## Remove non-piloting countries

```{r message=FALSE, comment = ""}

## Look at all country
#table(MainDataFrame$monit.progres_CountryofAsylum, useNA = "ifany")
#######
ctry <- as.data.frame(levels(as.factor(MainDataFrame$monit.progres_CountryofAsylum)))
names(ctry) <- "country"

## Keep only the pilot countries
ctry <- as.data.frame(ctry[ ctry$country %in% c("Argentina",
                                                # "Aruba",
                                                #  "Belize",
                                                "Chile",
                                                "Ecuador",
                                                # "Guatemala",
                                                #  "notsaid",
                                                # "Panama",
                                                "Peru",
                                                "RepublicaDominicana"), ])
names(ctry) <- "country"
#names(MainDataFrame)

MainDataFrame <- MainDataFrame[MainDataFrame$monit.progres_CountryofAsylum %in% as.character(ctry$country),  ]
cat("check after cleaning")
table(MainDataFrame$monit.progres_CountryofAsylum, useNA = "ifany")
nrow(MainDataFrame)

```

## Remove testing data

```{r message=FALSE, comment = ""}
## For Peru,  remove any date before 20-22 May (any date before this is a test)
# Number of records in the main data frame: 141 – total # of records is 136 (see bullet points #2 and #3)
# Period of data collection: between 2020-05-13 and 2020-05-23 – Period us between 20 and 26 May (any date prior is a test, the record submitted on 26 may was a whatsapp questionnaire)

##check that date are correctly recognized
#str(MainDataFrame$today) 
#str(MainDataFrame$start) 

MainDataFrame2 <- MainDataFrame[ (MainDataFrame$monit.progres_CountryofAsylum == "Peru" & 
                                 MainDataFrame$start < "2020-05-20") ,  ]
#  tests interviews were done on 14 and 15 May in Peru
table(MainDataFrame2$monit.progres_CountryofAsylum, MainDataFrame2$start , useNA = "ifany")

## Cleam from workpsace
rm(MainDataFrame2)
## We remove with ! for exclude
MainDataFrame <- MainDataFrame[ !(MainDataFrame$monit.progres_CountryofAsylum == "Peru" & 
                                    MainDataFrame$start < "2020-05-20") ,  ]

nrow(MainDataFrame)
```
## Remove if not crossed a border

```{r message=FALSE, comment = ""}
MainDataFrame <- MainDataFrame[ which(MainDataFrame$monit.crossedborder == "yes")  ,  ]
nrow(MainDataFrame)

```


## Saving raw data per country

```{r message=FALSE, comment = ""}
for (i in 1:nrow(ctry)) {
  ctryfilter <- as.character(ctry[ i , 1])
  MainDataFramesplit <- MainDataFrame[MainDataFrame$monit.progres_CountryofAsylum == ctryfilter,  ]
  write.csv(MainDataFramesplit, paste0(mainDirroot,"/data/MainDataFrame-",ctryfilter,"-raw.csv"), row.names = FALSE)
}

```

## Attention question

The attention was set up to ensure respondent are correctly reading questions

```{r message=FALSE, comment = ""}

table(MainDataFrame$attentionpass, useNA = "ifany")

# MainDataFrame <- MainDataFrame[ which(MainDataFrame$attentionpass == "Yes")  ,  ]
# nrow(MainDataFrame)
```

## Arrived before departed

This shall probably requires a new specific constraint in the collection 

Note that monit.checktimediff is counted on days while other are months 

```{r message=FALSE, comment = ""}

#	Check column AF “time in transit”… column AD is time since leaving the country (see highlighted example: the person left in 2016, thus 45 months),
#column AE is time in current location (Peru. E.g 25 months) while column AF is time in transit (590 months? days?). Important to put the measuring unit in the SOP  
# Months in transit – has negative number
## Check if arrived is before depart
MainDataFrame$Departbeforearrived <-  ifelse(MainDataFrame$monit.ArriveHere >= MainDataFrame$monit.DepartureDate, "Yes", "No" )

table(MainDataFrame$Departbeforearrived, useNA = "ifany")


head(MainDataFrame[ MainDataFrame$Departbeforearrived == "No" ,c( "monit.ArriveHere", "monit.DepartureDate", 
          "monit.TimeStayHere", #round((decimal-date-time(${today}) - decimal-date-time(${ArriveHere})) div 30.45, 0)
          "monit.TimeDeparted"  , #round((decimal-date-time(${today}) - decimal-date-time(${DepartureDate})) div 30.45, 0)
          "monit.checktimediff"  #decimal-date-time(${ArriveHere}) - decimal-date-time(${DepartureDate})
                       )], 10)
MainDataFrame <- MainDataFrame[ which(MainDataFrame$Departbeforearrived == "Yes")  ,  ]

nrow(MainDataFrame)
```

# Household size calculation

```{r message=FALSE, comment = ""}

# View(MainDataFrame[ ,c("monit.progres_groupsize",                                                 
#                       "monit.a.b.checktotal",                                         
#                       "monit.a.progres_TotalAdult", 
#                       
#                       "monit.a.progres_TotalAdultFemale",                                  
#                       "monit.a.progres_TotalAdultMale",                                     
#                       "monit.a.checkadult",      

## coalesce(${progres_totaladultfemale1859},0)+coalesce(${progres_totaladultfemale60},0)+coalesce(${progres_totaladultmale1859},0)+coalesce(${progres_totaladultmale60},0)

#                       "monit.a.b.checkadult1",       
#                                                                                                      
#                       "monit.a.progres_TotalMinor",          
#                       "monit.a.progres_TotalMinorFemale",                                  
#                       "monit.a.progres_TotalMinorMale",                                
#                       "monit.a.checkminor1",                                                 
#                       "monit.a.b.checkminor",                                              
#                       "monit.a.b.checkminor2",                
#                       
#                       "monit.a.progres_totaladultfemale1859",                              
#                       "monit.a.progres_totaladultfemale60",                                
#                       "monit.a.progres_totaladultmale1859",                                
#                       "monit.a.progres_totaladultmale60",                      
#                       "monit.a.progres_totalminorfemale04",                                
#                       "monit.a.progres_totalminorfemale511",                               
#                       "monit.a.progres_totalminorfemale1214",                              
#                       "monit.a.progres_totalminorfemale1517",                              
#                       "monit.a.progres_totalminormale04",                                  
#                       "monit.a.progres_totalminormale511",                                 
#                       "monit.a.progres_totalminormale1214",                                
#                       "monit.a.progres_totalminormale1517",                               
#                       "monit.a.couldwork"   
#                       )])

# Calculation check – checkminor – review the flag in raw data
#  the sum of adults and children is 560 while the total number of people in the HHs is 557
# The sum of boys and girls does not add up. 
# Check potential for error in the total # of girls and boys.  
# When adding up the age groups for girls, we get a total of 120 girls while the real number is 116. 
# This could be due to mistakes while filling up the questionnaire. 
# Worth reviewing. When adding up the age groups for boys, the total is 117 but should be 122.  
# Overall, it is important to check the sequence/flags/totals of men, women, girls and boys

```

## Check if sum is matching

```{r message=FALSE, comment = ""}
## Check adult is matching
MainDataFrame$summatching <-  ifelse(MainDataFrame$monit.progres_groupsize == MainDataFrame$monit.a.checkadult + MainDataFrame$monit.a.checkminor1, "Yes", "No" )

table(MainDataFrame$summatching , useNA = "ifany")

```

```{r message=FALSE, comment = ""}

MainDataFrame$summatchinggap <-  MainDataFrame$monit.progres_groupsize - MainDataFrame$monit.a.checkadult - MainDataFrame$monit.a.checkminor1

table(MainDataFrame$summatchinggap , useNA = "ifany")

```


## Check adult sum is matching

```{r message=FALSE, comment = ""}
## Check adult is matching
MainDataFrame$adultmatching <-  ifelse(MainDataFrame$monit.a.progres_TotalAdult == MainDataFrame$monit.a.checkadult, "Yes", "No" )

table(MainDataFrame$adultmatching , useNA = "ifany")

```

```{r message=FALSE, comment = ""}

MainDataFrame$adultmatchinggap <-  MainDataFrame$monit.a.progres_TotalAdult - MainDataFrame$monit.a.checkadult

table(MainDataFrame$adultmatchinggap , useNA = "ifany")

```


## Check minor sum is matching

```{r message=FALSE, comment = ""}
## Check adult is matching
MainDataFrame$minortmatching <-  ifelse(MainDataFrame$monit.a.progres_TotalMinor == MainDataFrame$monit.a.checkminor1, "Yes", "No" )

table(MainDataFrame$minortmatching , useNA = "ifany")

```
```{r message=FALSE, comment = ""}

MainDataFrame$minormatchinggap <-  MainDataFrame$monit.a.progres_TotalMinor - MainDataFrame$monit.a.checkminor1

table(MainDataFrame$minormatchinggap , useNA = "ifany")

```

## Check double non matching

```{r message=FALSE, comment = ""}

table(MainDataFrame$adultmatching, MainDataFrame$minortmatching , useNA = "ifany")

```

## Remove double non matching

```{r message=FALSE, comment = ""}

MainDataFrame <- MainDataFrame[ which(MainDataFrame$adultmatching == "Yes" &
                                       MainDataFrame$minortmatching == "Yes" ), ]

nrow(MainDataFrame)

```

## Filling admin 1 based on coordinates

For those who shared precise location

```{r message=FALSE, comment = ""}

#monit.progres_CoAadmin1
# "monit.shareloc"                                                    
# "location"                                                          
# "monit._location_latitude"                                          
# "monit._location_longitude" 



```



# Addressing issue with or_other

There is an issue in kobo  when using the or_other - the variable is set to NA - and the automatically offers field  specify is not compulsory  so we replace all NA by other 

## Protection incidents

 

```{r message=FALSE, comment = ""}

# Out of the 40 interviews that reported having suffered protection incidents, 7 did not mention what type of protection incident. 
# Since the question of types of protection incidents is mandatory 
# when interviewees answer that they did suffer protection incidents, would this be an issue with the Kobo form? 
# Only 1 of these 7 records had the place where the incident happened. 

table(MainDataFrame[ (is.na(MainDataFrame$monit.RouteIncidentType) & 
                        MainDataFrame$monit.RouteIncident =="yes" ), 
                     c("monit.progres_CountryofAsylum")], useNA = "ifany")   

MainDataFrame$monit.RouteIncidentType[ (is.na(MainDataFrame$monit.RouteIncidentType) &  MainDataFrame$monit.RouteIncident =="yes" )] <- "other"
 
```
##	Documentation

Same issue 

This needs more investigation - what were mostly the "other" that were offered as options form the question?

```{r message=FALSE, comment = ""}

###	Documentation: 

table(MainDataFrame$monit.documentation, useNA = "ifany")

cat("Breakdown of other per country")
table(MainDataFrame[ is.na(MainDataFrame$monit.documentation), c("monit.progres_CountryofAsylum")], useNA = "ifany")  

MainDataFrame$monit.documentation[ (is.na(MainDataFrame$monit.documentation)  )] <- "other"

# table(MainDataFrame$monit.documentation, MainDataFrame$monit.progres_CountryofAsylum, useNA = "ifany")    
# table(MainDataFrame[ is.na(MainDataFrame$monit.documentation), c("final.accessq")], useNA = "ifany") 

```

## Question on type of permit

same issue on other..

```{r message=FALSE, comment = ""}

MainDataFrame$monit.docResidence[ (is.na(MainDataFrame$monit.docResidence)  )] <- "other"
table(MainDataFrame$monit.docResidence, MainDataFrame$monit.progres_CountryofAsylum, useNA = "ifany")   

# Specific types of permits for Peru are not appearing in the dataset. Although we understand the categories,
# if you are going to create categories for multiple countries, it would be important to put what is equivalent to what in an annex in the SOP.

```


## Question  SocialBenefit
 9/16. Are you currently receiving some social protection (cash allowance) in the place where you are staying now?"
Many other there as well!
 
```{r message=FALSE, comment = ""} 
# Question 9/16:SocialBenefit

MainDataFrame$VulnerabilityScoring.CopingCapacity.SocialBenefit[ (is.na(MainDataFrame$VulnerabilityScoring.CopingCapacity.SocialBenefit)  )] <- "other"
table(MainDataFrame$VulnerabilityScoring.CopingCapacity.SocialBenefit, MainDataFrame$monit.progres_CountryofAsylum, useNA = "ifany") 

#table(MainDataFrame$VulnerabilityScoring.CopingCapacity.SocialBenefit, useNA = "ifany")
# <NA>    151 
```

## Question on coping mechanisms

```{r message=FALSE, comment = ""}
# Question on coping mechanisms: only 123 out of 127 answers. This question was mandatory
#table(MainDataFrame$VulnerabilityScoring.CopingCapacity.CopingMechanism, useNA = "ifany")
## <NA> 147

MainDataFrame$VulnerabilityScoring.CopingCapacity.CopingMechanism[ (is.na(MainDataFrame$VulnerabilityScoring.CopingCapacity.CopingMechanism)  )] <- "other"
#table(MainDataFrame$VulnerabilityScoring.CopingCapacity.CopingMechanism, MainDataFrame$monit.progres_CountryofAsylum, useNA = "ifany") 


table(MainDataFrame[ MainDataFrame$VulnerabilityScoring.CopingCapacity.CopingMechanism == "other", c("monit.progres_CountryofAsylum")], useNA = "ifany")   

  
```

# Question CopingCapacity: statushead calculation

This question was asked only on those who made gave a consent for scoring


Note that the question is raised only for those who have shared consent for scoring

```{r message=FALSE, comment = ""}
# Column VulnerabilityScoring.CopingCapacity.statushead  
table(MainDataFrame$VulnerabilityScoring.CopingCapacity.statushead, MainDataFrame$ConsentScore, useNA = "ifany")

```

```{r message=FALSE, comment = ""}
table(MainDataFrame$monit.progres_CountryofAsylum, MainDataFrame$ConsentScore, useNA = "ifany")
```

Check Result calculation


> if((${ageRange}='15-17' or ${ageRangeother}= '15-17'),
>    'child',
>    if((${ageRange}='over60' or
>        ${ageRangeother}='over60' or
>        selected(${SpecificNeeds}, 'disability') or
>        selected(${SpecificNeeds},'treatment') or
>        selected(${SpecificNeeds},'elderly')), 
>        'elderly-or-disabled',
>          if((${progres_Sex}='female' or ${progres_Sexother}='female'),
>             'female',
>             if((${maritalStatus}='single' or
>              ${maritalStatusother}='single' or
>              ${maritalStatus}='widow' or
>              ${maritalStatusother}='widow' or
>              ${maritalStatus}='divorced' or
>              ${maritalStatusother}='divorced'),
>              'single',
>             'male'))))

```{r message=FALSE, comment = ""}

## Look at 10 lines
MainDataFrame[ 1-10,
                     c( "VulnerabilityScoring.CopingCapacity.statushead",
                        "monit.SpecificNeeds", 
                        "VulnerabilityScoring.CopingCapacity.maritalStatus",
                        "VulnerabilityScoring.CopingCapacity.maritalStatusother",
                        "VulnerabilityScoring.CopingCapacity.ageRange"  , 
                        "VulnerabilityScoring.CopingCapacity.ageRangeother" ,  
                        "VulnerabilityScoring.CopingCapacity.progres_Sex" ,  
                        "VulnerabilityScoring.CopingCapacity.progres_Sexother"   )]

```

# Final Dataset

## Data collection channel per country

```{r message=FALSE, comment = ""}
table(MainDataFrame$monit.progres_CountryofAsylum, MainDataFrame$final.accessq, useNA = "ifany")

```

## Saving cleaned data per country

```{r message=FALSE, comment = ""}
for (i in 1:nrow(ctry)) {
  ctryfilter <- as.character(ctry[ i , 1])
  MainDataFramesplit <- MainDataFrame[MainDataFrame$monit.progres_CountryofAsylum == ctryfilter,  ]
  write.csv(MainDataFramesplit, paste0(mainDirroot,"/data/MainDataFrame-",ctryfilter,"-cleaned.csv"), row.names = FALSE)
}

```


# Data Weighting

```{r message=FALSE, comment = ""}
### Create weights. Values taken from popdata. 

# Since sampling was done on households, I estimate the number of households looking at average household size.
avg_hh_size <- mean(MainDataFrame$monit.progres_groupsize, na.rm = TRUE)

# get number of records
n_records <- nrow(MainDataFrame)

MainDataFrame$country <- MainDataFrame$monit.progres_CountryofAsylum

# create weights
MainDataFrame <- mutate(MainDataFrame, 
                        weight = case_when(
                          country == "Argentina" ~ (185711 / avg_hh_size) / n_records,
                          #country == "aruba" ~ (17008 / avg_hh_size) / n_records,
                          #country == "brazil" ~ (363676 / avg_hh_size) / n_records,
                          country == "Chile" ~ (465383 / avg_hh_size) / n_records,
                          #country == "colombia" ~ (2181002 / avg_hh_size) / n_records, 
                          #country == "costa_rica" ~ (114304 / avg_hh_size) / n_records,
                          country == "Ecuador" ~ (453694 / avg_hh_size) / n_records,
                          #country == "guatemala" ~ (111648 / avg_hh_size) / n_records,
                          #country == "honduras" ~ (6186 / avg_hh_size) / n_records,
                          #country == "panama" ~ (136007 / avg_hh_size) / n_records,
                          country == "Peru" ~ (867821 / avg_hh_size) / n_records,
                          country == "RepublicaDominicana" ~ (34549 / avg_hh_size) / n_records #,
                          #country == "trinidad_y_tobago" ~ (27552 / avg_hh_size) / n_records,
                          #country == "uruguay" ~ (28630 / avg_hh_size) / n_records,
                          #country == "venezuela" ~ (503444 / avg_hh_size) / n_records
                          )
)

table(MainDataFrame$weight, MainDataFrame$country, useNA = "ifany")

```


# Anonymisation


```{r message=FALSE, comment = ""}

library(sdcMicro)

# identify obs with highest individual risk
risky_observations <- function(sdc_obj, risk_threshold, vars_selected){
  observations <- extractManipData(sdc_obj)[vars_selected]
  individual_risks <- sdc_obj@risk$individual
  observations <- cbind(observations, individual_risks)
  observations <- observations[observations$risk >= risk_threshold, ]
  observations <- observations[order(observations$risk, decreasing = TRUE) , ]
  observations$risk <- percent(observations$risk, accuracy=0.001)
  observations$hier_risk <- percent(observations$hier_risk, accuracy=0.001)
  return (observations)
}

```

## Removing identifiers

```{r message=FALSE, comment = ""}

# create year and month of monitoring, remove exact date as it may lead to disclosure
MainDataFrame$year_of_monitoring <- substr(MainDataFrame$today, 7, 10)
MainDataFrame$month_of_monitoring <- substr(MainDataFrame$today, 4, 5)

MainDataFrame$submission_id <- MainDataFrame$"_id"

# remove variables that are notes, intermediairy calculation too sensitive or potential identifiers...
variables_to_remove <- c(
 "start",                                                             
  "end",                                                               
  "today",                                                               
  "deviceid",                                                          
  "subscriberid",                                                      
  "simserial",                                                         
  "phonenumber",                                                       
  "username",                                                          
  "email",                                                             
  "start_mins",                                                        
  "end_mins1",                                                         
  "survey_mins1",                                                      
  "end_mins3",                                                         
  "survey_mins3",                                                      
  "end_mins4",                                                         
  "survey_mins4",                                                      
  "logo",                                                              
  "ConsentInterview2",                                                 
  "ConsentInterview1",                                                 
  "screen.YesDisplaced",                                               
  "screen.DisplacedNo",                                                
  "screen.YesOver15",                                                  
  "screen.Over15No",                                                   
  "screen.ConsentIInterview3",                                         
  "screen.Consent",                                                    
  "monit.crossedborder" ,
 "monit.DepartureDate" ,                                              
 "monit.DepartureDateIDP",                                            
 "monit.ArriveHere",
  "monit.Monthhere" ,
 
  "monit.a.checkadult", 
  "monit.a.checkminor1",                                               
  "monit.a.couldwork",                                                 
  "monit.a.b.checktotal",                                              
  "monit.a.b.checkadult1",                                             
  "monit.a.b.checkminor",                                              
  "monit.a.b.checkminor2", 

 "monit.progres_CountryofAsylum1", 
 "monit.progres_CountryofAsylum2" , 
 "monit._location_latitude",                                          
 "monit._location_longitude",                                         
 "monit._location_altitude",                                          
 "monit._location_precision" ,   
 "monit.MonitoringCityTown" ,
 "ConsentScore",                                                      
  "needassistno" ,
 "VulnerabilityScoring.vulnote" ,
  "VulnerabilityScoring.WellBeing.attentioncheck",
 "VulnerabilityScoring.ConsentReg" ,                                  
  "VulnerabilityScoring.ConsentRegNo", 
  "preregister.noteregister",                                          
  "preregister.progres_givenname",                                     
  "preregister.progres_familyname",                                    
  "preregister.progres_dateofbirth",                                   
 "preregister.progres_phonenumber",                                   
 "preregister.phone_type",                                            
 "preregister.whatsapp",                                              
"preregister.formid",                                                
 "preregister.notreg",                                                
 "final.othercoment",                                                 
 "final.notefin",                                                   
 "final.codepartner",   
 "attentionpass",                                                     
 "_id",                                                               
 "_uuid",                                                             
 "_submission_time",                                                  
 "_validation_status",                                                
 "_index", 
"basicneedsMeals",                                                   
 "basicneedsShelter",                                                 
 "basicneedsWater",                                                   
 "basicneedsBathroom",                                                
 "basicneedsElectricity",                                             
 "basicneeds",                                                        
 "basicneedsscore",                                                   
 "copingHHHead",                                                      
 "copingDependency",                                                  
 "copingDisability",                                                  
 "copingWork",                                                        
 "copingNegmechanism",                                                
 "coping",                                                            
 "copingscore",                                                       
 "wellbeingSafety",                                                   
 "wellbeingDocumentation",                                            
 "wellbeingCommunication",                                            
 "wellbeingIsolation",                                                
 "wellbeing",                                                         
 "wellbeingscore"  
)
MainDataFrame2 <- select(MainDataFrame, - all_of(variables_to_remove))
```

## Defining key variables

```{r message=FALSE, comment = ""}

# define key variables for disclosure scenario
key_variables <- c(

  "monit.nationality",                                                 
 "monit.progres_CountryofAsylum", 
"monit.progres_CoAadmin1" ,

  "monit.TimeDeparted",                                                
  "monit.TimeStayHere",                                                
  "monit.checktimediff",  
  
  
  "monit.progres_groupsize" ,                                          
  "monit.a.progres_TotalAdult",                                        
  "monit.a.progres_TotalAdultFemale",                                  
  "monit.a.progres_TotalAdultMale",                                    
  "monit.a.progres_totaladultfemale1859",                              
  "monit.a.progres_totaladultfemale60",                                
  "monit.a.progres_totaladultmale1859",                                
  "monit.a.progres_totaladultmale60",                                 
  "monit.a.progres_TotalMinor",                                        
  "monit.a.progres_TotalMinorFemale",                                  
  "monit.a.progres_TotalMinorMale",                                    
  "monit.a.progres_totalminorfemale04",                                
  "monit.a.progres_totalminorfemale511",                               
  "monit.a.progres_totalminorfemale1214",                              
  "monit.a.progres_totalminorfemale1517",                              
  "monit.a.progres_totalminormale04",                                  
  "monit.a.progres_totalminormale511",                                 
  "monit.a.progres_totalminormale1214",                                
  "monit.a.progres_totalminormale1517", 
 
  "monit.householdLeftbehind",
  "monit.prevdeport" ,
  
    "monit.intentionspctr" ,                                             
  "monit.intentionsptown" ,
  "monit.SpecificNeeds" ,                                              
  "monit.SpecificNeeds.disability",                                    
  "monit.SpecificNeeds.treatment",                                     
  "monit.SpecificNeeds.treatmentyesaccess",                            
  "monit.SpecificNeeds.unacompanied",                                  
  "monit.SpecificNeeds.elderly",                                       
  "monit.SpecificNeeds.pregnant",                                      
  "monit.SpecificNeeds.lactating",                                     
  "monit.SpecificNeeds.minorhead",                                     
  "monit.SpecificNeeds.victimsurvivor"
)

```

## Set up sdcMicro object

```{r message=FALSE, comment = ""}

frame_sdc_obj <- createSdcObj( dat = MainDataFrame2,
                               hhId = "submission_id",
                               keyVars = key_variables,
                               weightVar = "weight"
                            )

```



## Applying Data Anonymisation treatment

```{r message=FALSE, comment = ""}
# Local suppression to obtain k-anonymity
frame_sdc_obj_3 <- kAnon(frame_sdc_obj, importance=NULL, combs=NULL, k=c(3))

```



```{r message=FALSE, comment = ""}
print(frame_sdc_obj_3, type = "recode")
```

```{r message=FALSE, comment = ""}
print(frame_sdc_obj_3, type = "ls")

```

## spliting and saving anonymised data per country

```{r message=FALSE, warning=FALSE, comment= ""}

# get anonymized dataset
MainDataFrame_anonymized <- extractManipData(frame_sdc_obj_3)

```



```{r message=FALSE, comment = ""}
for (i in 1:nrow(ctry)) {
  ctryfilter <- as.character(ctry[ i , 1])
  MainDataFramesplit <- MainDataFrame_anonymized[MainDataFrame_anonymized$monit.progres_CountryofAsylum == ctryfilter,  ]
  write.csv(MainDataFramesplit, paste0(mainDirroot,"/data/MainDataFrame-",ctryfilter,"-anonymised.csv"), row.names = FALSE)
}

```


