---
title: "Building Map Reference of Admin 1"
date: " `r format(Sys.Date(),  '%d %B %Y')`"
always_allow_html: yes
output:
  html_document:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    toc: yes
    toc_depth: 2
    toc_float: yes
    includes:
       in_header: css/header.html
---



<link rel="stylesheet" href="css/unhcr-bootstrap.css">
<link rel="stylesheet" href="css/style.css">
<link rel="stylesheet" href="css/unhcr-header.css">


# Building Map Reference of Admin 1

```{r loaddata, message=FALSE, warning=FALSE}
library("tidyverse")
library("sf")
library("rmapshaper")
library("geojsonio")
library("geojsonR")
library("rgdal")
library("readxl")
library("spdplyr")
library("lawn")
library("ggspatial")

mainDir <- getwd()
mainDirroot <- substring(mainDir, 0 , nchar(mainDir) - 5)

```


## Checking map from mapping.unhcr.org

```{r message=FALSE, comment = ""}
rgn = read_sf( dsn = paste0(mainDirroot,"/data/Americas_Admin1"), "Americas_admin1")

## Checking size of file
pryr::object_size(rgn)

## quite too big for easy computation

## Trying to simplify it
##rgn_simp = rmapshaper::ms_simplify(rgn, keep = 0.01) 

## Command is failing because of not cleaned geometry... cf Panama for instance - overlapping polygon...
```
this is quite too heave for statistical mapping... Generating the nmap below takes a long time...

```{r }
ggplot(rgn) + 
  geom_sf(color = "black", fill = "antiquewhite") + 
  theme(panel.grid.major = element_line(color = gray(.5), 
                                        linetype = 'dashed', size = 0.1), 
        panel.background = element_rect(fill = "aliceblue")) +
  xlab("Longitude") + ylab("Latitude") +
  ggtitle("Admin 1 unit in Americas - mapping.unhcr.org ", 
          subtitle = paste0("(",length(unique(rgn$pcode)), "  polygons )"))

```

## Let's extract the pcode that we need from this file

```{r message=FALSE, comment = ""}

rgndata <- as.data.frame(rgn[ , c("adm0name",   "iso3", "name", "pcode", "code_op" )])
# names(rgndata)
rgndata$geometry <- NULL
# 
write.csv(rgndata, paste0(mainDirroot,"/data/rgndata.csv"), row.names = FALSE)

```


## Getting data from Natural Earth

```{r message=FALSE, comment = ""}
tmp_dir = tempdir()
tmp     = tempfile(pattern = "", tmpdir = tmp_dir, fileext = ".zip")

download.file(
    paste0(
      "https://naciscdn.org/naturalearth/10m/cultural/",
      "ne_10m_admin_1_states_provinces.zip"
    ),
    destfile = tmp
)

unzip(tmp, exdir = tmp_dir)

#Read the shapefile:

rgne = read_sf(tmp_dir, "ne_10m_admin_1_states_provinces")
## Checking size of file
pryr::object_size(rgne)

## a lot better!!
```


## Clip to the Americas

```{r message=FALSE, comment = ""}

#view(lawn_bbox_polygon(c(-170, -60, -30, 170)))

rgne_clipped <- rmapshaper::ms_clip(rgne, bbox = c(-170, -60, -30, 170))



nrow(rgne_clipped)

pryr::object_size(rgne_clipped)
```

```{r}
ggplot(rgne_clipped) + 
  geom_sf(color = "black", fill = "antiquewhite") + 
  theme(panel.grid.major = element_line(color = gray(.5), 
                                        linetype = 'dashed', size = 0.1), 
        panel.background = element_rect(fill = "aliceblue")) +
  xlab("Longitude") + ylab("Latitude") +
  ggtitle("Admin 1 unit in Americas - Natural Earth", 
          subtitle = paste0("(",length(unique(rgn$pcode)), "  polygons )"))

```

## Remove countries from pacific

```{r }

ctry2 <- as.data.frame(unique(rgne_clipped[ ,c( "adm0_a3",  "admin"  )]))
ctry2$geometry <- NULL
ctry2 <- as.data.frame(unique(ctry2[ ,c( "adm0_a3",  "admin"  )]))

rgne_clipped <- rgne_clipped[ !(rgne_clipped$adm0_a3 %in% c("NIU", "ASM", "CLP", "COK", "PYF", "GRL" )), ]

ggplot(rgne_clipped) + 
  geom_sf(color = "black", fill = "antiquewhite") + 
  theme(panel.grid.major = element_line(color = gray(.5), 
                                        linetype = 'dashed', size = 0.1), 
        panel.background = element_rect(fill = "aliceblue")) +
  xlab("Longitude") + ylab("Latitude") +
  ggtitle("Admin 1 unit in Americas - Natural Earth", 
          subtitle = paste0("(",length(unique(rgn$pcode)), "  polygons )"))
```


## getting var to do the join

```{r message=FALSE, comment = ""}

## Extract name to do the join
rgne_clipped_data <- as.data.frame(unique(rgne_clipped[ ,c("iso_3166_2",  "adm1_code" , "name", "name_alt", "name_local", "woe_name" ,  "gn_name" , "gns_name", "adm0_a3",  "adm0_label"  )]))
rgne_clipped_data$geometry <- NULL
rgne_clipped_data <- as.data.frame(unique(rgne_clipped_data[ ,c("iso_3166_2", "adm1_code" ,"name", "name_alt", "name_local","woe_name" ,  "gn_name" , "gns_name", "adm0_a3",  "adm0_label"   )]))
```

## Testing the join 

```{r message=FALSE, comment = ""}

rgndata2 <- merge( x = rgndata  , y = rgne_clipped_data , by= "name")
nrow(rgndata2)

### Does not work - let's save it and do the mapping a la mano... sigh...
write.csv(rgne_clipped_data, paste0(mainDirroot,"/data/rgne_clipped_data.csv"), row.names = FALSE)

## Reading the mapping table
mappingpcode <- read.csv(paste0(mainDirroot,"/data/mappingpcode.csv"))

```
## Merging with pcode and office

```{r message=FALSE, comment = ""}
rgne_clipped_pcode <- merge (x = rgne_clipped, y = mappingpcode , by = "adm1_code" ,all.x= TRUE)

pryr::object_size(rgne_clipped_pcode)

## Check percent matching
nrow(rgne_clipped_pcode[!(is.na(rgne_clipped_pcode$pcode)), ]) 
nrow(rgne_clipped_pcode[!(is.na(rgne_clipped_pcode$pcode)), ]) / nrow(rgne_clipped_pcode)

```
So we went from 279Mb to 7 Mb 

## Saving file to GeoJson format

```{r message=FALSE, comment = ""}

rgne_clipped_pcode_json <- geojsonio::geojson_json(rgne_clipped_pcode)
geojsonio::geojson_write(rgne_clipped_pcode_json, 
                         file = paste0(mainDirroot,"/data/america_adm1.geojson"))
```

## Now let's simplify

```{r message=FALSE, comment = ""}
rgne_clipped_pcode_simp = rmapshaper::ms_simplify(rgne_clipped_pcode, keep = 0.5)
nrow(rgne_clipped_pcode_simp[!(is.na(rgne_clipped_pcode_simp$pcode)), ]) 
pryr::object_size(rgne_clipped)

```



## Saving file to GeoJson format

```{r message=FALSE, comment = ""}

rgne_clipped_pcode_simp_json <- geojsonio::geojson_json(rgne_clipped_pcode_simp)
geojsonio::geojson_write(rgne_clipped_pcode_simp_json, 
                         file = paste0(mainDirroot,"/data/america_simpadm1.geojson"))
```

## Check projection and transform to bind for comparison

```{r message=FALSE, comment=}
st_crs(rgn)

st_crs(rgne_clipped_pcode)

rgn2 <- st_transform(rgn, crs =  4326)

```

## Merge.

```{r message=FALSE, comment=}
rgn2$simplified <- "Original"
rgne_clipped_pcode$simplified      = "Clean-from-NE"
rgne_clipped_pcode_simp$simplified = "Simplified-with-Pcode"


rgne = reduce(
  list( 
        rgne_clipped_pcode[, c("name", "pcode","simplified")],
        #rgn2[, c("name", "pcode", "simplified")],
        rgne_clipped_pcode_simp[, c("name", "pcode","simplified")]),
  rbind
)
# rgne = bind_rows(
#    rgn2[, c("name", "pcode", "simplified")], 
#         rgne_clipped_pcode[, c("name", "pcode","simplified")], 
#         rgne_clipped_pcode_simp[, c("name", "pcode","simplified")])

```



```{r }
ggplot(rgne) + 
  geom_sf(color = "black", fill = "antiquewhite") + 
  facet_wrap( ~ simplified) +
  
  theme(panel.grid.major = element_line(color = gray(.5), 
                                        linetype = 'dashed', size = 0.1), 
        panel.background = element_rect(fill = "aliceblue")) +
  #coord_map("conic", lat0 = 30) +
  
  #theme_minimal() +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
        pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"),
        style = north_arrow_fancy_orienteering) +
  xlab("Longitude") + ylab("Latitude") +
  ggtitle("Admin 1 unit in Americas", 
          subtitle = paste0("(",length(unique(rgne_clipped_pcode$pcode)), " to ", length(unique(rgne_clipped_pcode_simp$pcode)), " polygons )"))

```

## Details

```{r }

ggplot(rgne) + 
  geom_sf(color = "black", fill = "lightgreen") + 
  facet_wrap( ~ simplified) +
  theme_minimal() +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
        pad_x = unit(0.2, "in"), pad_y = unit(0.2, "in"),
        style = north_arrow_fancy_orienteering) +
  xlab("Longitude") + ylab("Latitude") +
  ggtitle("Admin 1 unit in Central Americas") +
  coord_sf(xlim = c(-95, -75), ylim = c(7, 17), expand = FALSE)

```


